Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Moved Figure 1 to top-right corner

	\title{Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search}
	\author{
		Thom van der Woude$^1$\\[2ex]
		\normalsize{Supervisors: Jesse Mulderij$^1$ Mathijs de Weerdt$^1$}
	}
	\date{
		$^1$TU Delft\\
		t.b.vanderwoude@student.tudelft.nl\\\{j.mulderij, m.m.deweerdt\}@tudelft.nl\\[2ex]
		\today
	}

@@

	As observed by \cite{ma2016b}, in real-world applications of MAPF such as warehouse robotics \cite{wurman2007} goals are often assigned to teams of agents instead of single agents as in standard MAPF. Using MAPF in such applications requires pre-assignment of goals to agents using the Hungarian Algorithm \cite{kuhn55} or similar methods, but such approaches are suboptimal as the true cost of a given matching can only be found by solving the corresponding MAPF instance. Ma and Koenig \cite{ma2016} formulate the joint problem of finding the optimal makespan solution across all possible matchings as the combined target-assignment and pathfinding (TAPF) problem. They also present the Conflict-Based Min-Cost-Flow (CBM) algorithm for solving TAPF.

	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}. The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios such as the Moving AI maps \cite{sturtevant2012}.

@@

	\section{Multi-agent Pathfinding with Matching} % Problem description
	\label{mapfm}
	\begin{wrapfigure}[19]{r}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Edge conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\vspace{-10pt}
		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019}).}\label{fig:conflicts}
	\end{wrapfigure}

>>>>

	\title{Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search}
	\author{
		Thom van der Woude$^1$\\[2ex]
		\normalsize{Supervisors: Jesse Mulderij$^1$ Mathijs de Weerdt$^1$}
	}
	\date{
		\normalsize{$^1$TU Delft\\
		t.b.vanderwoude@student.tudelft.nl\\\{j.mulderij, m.m.deweerdt\}@tudelft.nl\\[2ex]
		}
	}

@@

	As observed by \cite{ma2016b}, in real-world applications of MAPF such as warehouse robotics \cite{wurman2007} goals are often assigned to teams of agents instead of single agents as in standard MAPF. Using MAPF in such applications requires pre-assignment of goals to agents using the Hungarian Algorithm \cite{kuhn55} or similar methods, but such approaches are suboptimal as the true cost of a given matching can only be found by solving the corresponding MAPF instance. 
	\begin{wrapfigure}[21]{r}{.25\textwidth}
		\vspace{-10pt}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Edge conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\vspace{-10pt}
		\caption{Two types of conflict between agents from \cite{stern2019}.}\label{fig:conflicts}
	\end{wrapfigure}
	Ma and Koenig \cite{ma2016} formulate the joint problem of finding the optimal makespan solution across all possible matchings as the combined target-assignment and pathfinding (TAPF) problem. They also present the Conflict-Based Min-Cost-Flow (CBM) algorithm for solving TAPF. 
	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}. The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios such as the Moving AI maps \cite{sturtevant2012}.

@@

	\section{Multi-agent Pathfinding with Matching} % Problem description
	\label{mapfm}
